---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Open Time Series: Human-Friendly, Machine Readable Time Series

<!-- badges: start -->
<!-- badges: end -->

The primary goal of the opentimeseries R package is to conveniently
read time series and there meta information from *opentsi* style archives.
While Open Time Series Initiative archives use git to manage different
versions of time series and GitHub as a remote data store, reading data
does not require git to be installed on your local machine. 


## Installation

You can install the development version of opentimeseries from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("opentsi/opentimeseries")
```

## Basic Usage

Given a unique time series identifier and a GitHub repo, *opentimeseries*
will return a time series and long format `data.table`. 


```{r example}
library(opentimeseries)
a <- read_open_ts("ch.kof.globalbaro.leading",
                  remote_archive = "opentsi/kofethz")
a
```

By specifying a date in addition, you can able to obtain other versions but
the most recent one. The *opentimeseries* package will simply select
the most recent release that was available at the selected date. 

```{r}

a202307 <- read_open_ts("ch.kof.globalbaro.leading",
                        date = "2023-07-01")

```

Because time series data can get revised, storing vintages is important to monitor 
data revisions and benchmark forecasts. Here's a quick visual comparison: 


```{r}
library(tsbox)
a202307$id <- sprintf("%s.202307", a202307$id)
a$id <- sprintf("%s.%s", a$id, Sys.Date())
ts_plot(rbind(a202307,a))

```


## Get Entire History of a Time Series

